Application-Level Regression Testing Framework using Jenkins

### 2017-03-23 manuscript/manuscript.tex
Worked on describing master-node using Jenkins built-in node.

%\begin{abstract}
%LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. We evaluated test frameworks such as Inca [1] and Jenkins [2]. Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.

%Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.

%In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters. We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests. The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
%\end{abstract}

@@

Monitoring large and complex high-performance computing systems have many challenges. Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity. Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.

Over time, either due to configuration and software changes or hardware aging, performance of such complex system may regress. To identify and correct such regression, one must have some method to do regression testing of the system performance. This requires a systematic record of the system performance over time.

@@

Jenkins is an open source automation server. Although it is typically used as a continuous integration tool in the software development process, its wide-ranging features makes it suitable for any task that can be automated. These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts. We chose Jenkins as the tool for our regression testing framework because of its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.

In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS). These systems are Cray XE, XK, XC, and CS series. The outline of this paper is as follows. [NEED TO WRITE THIS]

@@

Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software. In our case, this is not what we would want. In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e. via batch job submission to the job queueing system). This is because not only do we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly. Incidentally, the latter also informs us of any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions. In short, we want our tests to simulate typical workflow of a user on the system being testing.

Therefore what we need is a mechanism to execute a ``project'' --- a user-configured description of work which Jenkins should perform such as building a piece of software, in Jenkins jargon --- on remote machines (``remote'' from the perspective of Jenkins). In this case, the Jenkins machine simply manages the automation scheduling, shows status of projects in execution (``builds'' in Jenkins jargon) , and archives results of the tests (i.e. ``artifact''). It also provides the user interface (via its own web server) to create and configure projects. These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the truly heavy lifting of building and executing the application tests are performed on the remote machine.

There are two ways to achieve an executing build on a remote machine. Each have their own benefits, and your selection is a matter of choice. One may use Jenkin's core feature of adding ``Nodes`` to its environment. One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on a remote machine via SSH protocol. At NICS our setup uses the former, while at NCSA our setup uses the latter. In the following we briefly discuss the setup of these two mechanisms.

@@

\subsection{Configuration Choices}
The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind Apache HTTP Server with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).

>>>>

\begin{abstract}
LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. We evaluated test frameworks such as Inca [1] and Jenkins [2]. Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.

Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.

In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters. We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests. The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
\end{abstract}

@@

Monitoring large and complex high-performance computing systems has many challenges. Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity. Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.

Over time, either due to configuration changes or hardware aging, performance of such complex system may regress. To identify and correct such regression, one must have some method to do regression testing of the system performance. This requires systematic record of the the system performance over time.

@@

Jenkins is an open source automation server. Although it is typically used as continuous integration tool in software development process, its wide-ranging features makes it suitable for any task that can be automated. These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts. We chose Jenkins as the tool for our regression testing framework because its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.

In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Application, Darter and Beacon at the National Institute for Computational Sciences (NICS). These systems are Cray XK, XC, and CS series. The outline of this paper is as follows. [FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT]

@@

Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software. In our case, this is not what we would want. In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e. via batch job submission to the job queueing system). This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly. Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions. In short, we want our tests to simulate typical workflow of a user on the system being testing.

Therefore what we need is a mechanism to execute a ``project'' --- a user-configured description of work which Jenkins should perform such as building a piece of software, in Jenkins parlance --- on remote machines (``remote'' from the perspective of Jenkins). In this case, the Jenkins machine simply manages the automation scheduling, shows status of projects in execution (``builds'' in Jenkins parlance) , and archives results of the tests (i.e. ``artifact''). It also provides the user interface (via its own web server) to create and configure projects. These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the trully heavy lifting on building and executing the application tests are done on the remote machine.

There are two ways to achieve executing builds on remote machine. Each has their own benefits, and whichever way to use is a matter of choice. One may use Jenkin's core feature of adding ``Nodes`` to its environment. One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on remote machine via SSH protocol. At NICS our setup uses the former, while at NCSA our setup uses the latter. In the following we briefly discuss the setup of these two mechanisms.

\subsection{Using Nodes for Test Systems}
The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do. As projects are added, one can add nodes (i.e. more build machines) allowing Jenkins to build more projects concurrently. Jenkin's project can also be explicitly 'labeled' to only be executed on a certain node. We capitalized both of these features to enable the aforementioned remote execution.

For each HPC system login node, we created a Jenkins node\footnote{Do not be confused with multiple usage of the word ''node`` here. The former refers to the typical usage of login node in HPC. The latter refers to Jenkins' vernacular of ''node`` as previously defined}. We then labeled the (Jenkins) node with the name of the HPC system. For example, at NICS we have the labels 'beacon' and 'darter' to refer to the Cray CS-300 (Beacon) and XC-30 (Darter) login nodes, respectively. Each test application (i.e. ''project``) is then labeled to ensure that they only run on the appropriate node. For example, we have used NAMD (FIXME: Need reference for NAMD) as an applicaton test. We would create a Jenkin project called ''NAMD-Beacon`` and label it to only run on ''beacon`` node. We would also create another project called ''NAMD-Darter`` and label it appropriately. The two projects have slighly different build scripts (and possibly different test cases) so that they build correctly on the systems they were meant to run on.

Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connect back to the master via a certain port (which is configurable). This can be considered a drawback. If the daemon somehow dies, it needs to be restarted. The daemon runs as regular user, the user which essentially runs the build and submit the jobs on the HPC system. In our case, we created a user called ''jenkins`` with the same privilege as any other regular user. Both the extra port opening and the daemon itself may be considered as attack vectors from security perspective. At NICS however we consider this to be acceptable because of other mitigation (which we will discussed later).

The benefit of this method is that one can basically treat the nodes as local environment in Jenkins, while having access to the HPC environment. For example, each node would have access to the parallel lustre filesystem mounted by the HPC system (even if Jenkins master itself does not, being only a small separate VM). Each node can define its lustre filesystem as its build and test workspace. Yet Jenkins automatically manages all communication with the nodes such that files (e.g. plot data, test output) generated on the lustre filesystem is readable from Jenkins without the explicit remote copy (i.e. via SCP). Another example is that one can have Jenkins checkout or clone code from remote repository (e.g. using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node. These benefits integration makes building Jenkins project more seamless.

@@

\subsection{Configuration Choices}
The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences and the National Center for Supercomputing Applications, funded by the National Science Foundation (NSF).
